### 2021-04-19 evaluation.tex
Add some todo discussion to comparison with PAAR results

\todo[inline,author=R2]{In your PAAR paper [7], the experimental results show that your linear model is not as good as the baseline but it is no longer the case here. How do you explain this? If it was further improved after PAAR, it should be mentioned.}

>>>>

\todo[inline]{R2: In your PAAR paper [7], the experimental results show that your linear model is not as good as the baseline but it is no longer the case here. How do you explain this? If it was further improved after PAAR, it should be mentioned.

FB: I think this is because here we evaluate on a different distribution of problems, one that is possibly more similar to the training set. In the PAAR paper, the test problems were sampled from problems with at most 1024 predicates in TPTP v7.2.0 ($\frac{15751}{16748}$ = \SI{94.05}{\percent}). Here, the test problems are sampled from problems with at most 100k nodes ($\frac{7658}{8526}$ = \SI{89.82}{\percent}) in TPTP v7.4.0. Should I discuss this in this paper? It seems of relatively little interest.}
